Simulation of seed dispersal distance - 100 runs

### 2020-10-12 appendixB/sim100/appendixB_100.Rmd
arranged all tables according to ldd n
changed title

---
title: "Simulation of seed dispersal distance - 10 runs"
author: "Javiera Rudolph"
output: 
  html_document:
    toc: true
    fig_width: 12
    fig_height: 6
---

@@

directory <- "appendixB/sim10/"

>>>>

---
title: "Simulation of seed dispersal distance - 100 runs"
author: "Javiera Rudolph"
output: 
  html_document:
    toc: true
    fig_width: 12
    fig_height: 6
---

@@

directory <- "appendixB/sim100/"
